Parsing Postfix log files

### 2007-10-09 doc/logparser.tex
Explained that rules are filtered according to the program which produced the log line. Mentioned that Postfix is separated into different programs which do one thing and do it well.

@@

@@

>>>>

Postfix's design follows the Unix philosophy of \textit{Write programs that
do one thing and do it well\/}~\cite{unix-philosophy}, and is separated
into various component programs to perform the tasks required of an MTA\@:
receive mail, send mail, local delivery of mail, etc. --- full details can
be found at~\cite{postfix-overview}.  Each log line contains the name of
the Postfix program which produced the log line, and this information is
used when determining which rules should be used to parse each log line
(see section~\ref{rule characteristics} for details.)

@@

\label{rule characteristics}

@@

    \item Rules are annotated with the name of a Postfix program, and will
        only be used when parsing log lines produced by that
        program.\footnote{There are also generic rules which are used when
        parsing log lines produced by any Postfix program, but only if
        there are also rules specific to that program, and those rules must
        already have been tried and failed.}  Any given rule will only be
        used to parse a subset of the log lines, and any given log line
        will only be parsed by a subset of the rules.
